Analytics without Tuning Considered Harmful?\\(Two Case Studies in Defect Prediction)

### 2015-02-18 tuningpredictor.tex
startting up

\documentclass{acm_proc_article-sp}
\usepackage{multirow}
\usepackage{color}
\usepackage{colortbl}
\usepackage{picture}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\newcommand{\quart}[3]{\begin{picture}(100,6)%1
{\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}

\begin{document}
\title{Tuning Learners before Applying: New Reflection in Defect Prediction }
\author{ A, B, C}
\maketitle
\begin{abstract}
Data mining techniques have been widely applied to software defect prediction with various 
empirical data sets. Those proposed leaners are always evaluated against the state of the art 
predictors by performing statistical analysis. Undoubtedly, given the bias from data sets and 
accuracy indicators, the newer predictors outperform counterparts in selected experimental 
settings. However,  most of data mining algorithm based predictors (e.g. CART, random 
forest, 
neural networks, SVM) have built-in {\it magic} parameters, like the number of trees in random 
forest algorithm. the impact of internal parameters in those methods have been neglected 
during evaluation. In this paper, we investigate this impact by tuning parameters in defect 
predictors with search-based software engineering algorithm. Specifically, we used differential 
evolution to tune the CART and a new predictor based on WHERE algorithm with local data, 
and then predictors with optimal parameters obtained from tuning process will be applied to 
predict defects. By comparing the performance of predictors with and without tuning process,  
we observe that tuning improves the predictors' performance and predictors woking with 
different data sets need different parameters. Our results also suggest that we should not use 
the predictors of the shelf with their default parameters and tuning should be a processor 
combined with any predictor with built-in parameters.

@@

% A category with the (minimum) three required fields
\category{D.2.9}{Software Engineering}{Management}[Cost estimation]

\terms{Experimentation, Algorithm}

\keywords{Defect prediction, Data Mining, Tuning Parameters, CART, WHERE} 
% NOT required for Proceedings

@@

Software has becoming a large and complex system and delivering reliable and quality 
software is imperative for development teams. Empirical study shows that the longer the 
defects exist in software systems, the more the cost of time and money it will take to fix it 
\textbf{ [need a ref]}. Therefore, project managers and software programers strive to find 
defects in their system as early as possible. Defect prediction has been investigated 
extensively in industrial and academia during the past two decades. As an important research 
field, building data miners  \cite{lessmann2008benchmarking, mccabe1976complexity, 
menzies2007data, menzies2010defect, jiang2008can, menzies2011local, song2011general} 
over static code features of software system has been demonstrated to be a way to predict 
which models are more likely to contain defects.

@@

\section{Acknowledgments}

>>>>

\documentclass{sig-alternative}
\usepackage{multirow}
\usepackage{color}
\usepackage{colortbl}
\usepackage{picture}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\newcommand{\quart}[3]{\begin{picture}(100,6)%1
{\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}

%% timm tricks
\newcommand{\bi}{\begin{itemize}[leftmargin=0.4cm]}
\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\tion}[1]{\S\ref{sect:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\eq}[1]{Equation~\ref{eq:#1}}

%% space saving measures

\usepackage[shortlabels]{enumitem} 
\usepackage{times}

\usepackage{url}
\def\baselinestretch{1}

\setlist{nosep}
 \usepackage[font={small}]{caption, subfig}
\setlength{\abovecaptionskip}{1ex}
 \setlength{\belowcaptionskip}{1ex}

 \setlength{\floatsep}{1ex}
 \setlength{\textfloatsep}{1ex}
\usepackage[compact,small]{titlesec}
\DeclareMathSizes{7}{7}{7}{7} 
\pagenumbering{arabic}
\setlength{\columnsep}{7mm}

\begin{document}

\conferenceinfo{FSE}{'15 Bergamo, Italy}
\title{Analytics without Tuning Considered Harmful?\\(Two Case Studies in Defect Prediction)}
\numberofauthors{1}
\author{
\alignauthor
Wei Fung, TimMenzies\\
       \affaddr{Computer Science, North Carolina State University, USA}\\
       {wfu@ncsu.edu, tim.menzies@gmail.com}}

\maketitle
\begin{abstract}
Data mining techniques have been widely applied to software defect prediction with various 
empirical data sets. Those proposed leaners are always evaluated against the state of the art 
predictors by performing statistical analysis. Undoubtedly, given the bias from data sets and 
accuracy indicators, the newer predictors outperform counterparts in selected experimental 
settings. However,  most of data mining algorithm based predictors (e.g. CART, random 
forest, 
neural networks, SVM) have built-in {\it magic} parameters, like the number of trees in random 
forest algorithm. the impact of internal parameters in those methods have been neglected 
during evaluation. In this paper, we investigate this impact by tuning parameters in defect 
predictors with search-based software engineering algorithm. Specifically, we used differential 
evolution to tune the CART and a new predictor based on WHERE algorithm with local data, 
and then predictors with optimal parameters obtained from tuning process will be applied to 
predict defects. By comparing the performance of predictors with and without tuning process,  
we observe that tuning improves the predictors' performance and predictors woking with 
different data sets need different parameters. Our results also suggest that we should not use 
the predictors of the shelf with their default parameters and tuning should be a processor 
combined with any predictor with built-in parameters.

@@

% A category with the (minimum) three required fields
\vspace{1mm}
\noindent
{\bf Categories/Subject Descriptors:} 
D.2.8 [Software Engineering]: Product metrics;
I.2.6 [Artificial Intelligence]: Induction

\vspace{1mm}
\noindent
{\bf General Terms:} Experimentation, Algorithm}

\vspace{1mm}
\noindent
{\bf Keywords:} defect prediction, CART, random forests,
Fastmap,   bootstrap sampling, effect size, A12.

@@

\begin{raggedleft}
{\em ``The  common misunderstanding about science 
is that scientists seek and find truth. They don't- 
they make and test models.''}\\ -- Neil Gershenfeld

{\em Essentially, all models are wrong, but some are useful."}\\ --George Box

\end{raggedleft}

How ``true'' are the  models generated by software analytics?
Suppose we use a model generated from software project data to, for example,
assess the relative value of OO metrics vs procedural metrics for predicting
project defects. Are we reporting ``truth'' in any sense of the word? And for home
many other projects might we find that same ``truth''?

Our reading of the

and we reflect on that model, are we

will it reveal the `1`t
A standard approach to software analutics
Software has becoming a large and complex system and delivering reliable and quality 
software is imperative for development teams. Empirical study shows that the longer the 
defects exist in software systems, the more the cost of time and money it will take to fix it 
\textbf{ [need a ref]}. Therefore, project managers and software programers strive to find 
defects in their system as early as possible. Defect prediction has been investigated 
extensively in industrial and academia during the past two decades. As an important research 
field, building data miners  \cite{lessmann2008benchmarking, mccabe1976complexity, 
menzies2007data, menzies2010defect, jiang2008can, menzies2011local, song2011general} 
over static code features of software system has been demonstrated to be a way to predict 
which models are more likely to contain defects.

@@

\section*{Acknowledgements}
This work was partially funded by an National Science
Foundation grant NSF-CISE 1302169.

\vspace*{0.5mm}
\scriptsize
